A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-10-06 inst/paper.Rnw
alpha still not showing

proteinnet <- merge(yeast.samp$vertices, yeast.samp$edges, by.x="label", by.y="from", all=TRUE)
@
<<yeast_ex, echo=TRUE, fig.cap="Protein in protein interation network in yeast.", cache=FALSE>>=
ggplot(data = proteinnet, aes(from_id = label, to_id = to)) +
  geom_net(alpha = .25, colour = 'magenta', layout = 'random',
           layout.par = list(dist = 'uniang')) +
  theme_net()
@

>>>>

proteinnet <- merge(yeast.samp$vertices, yeast.samp$edges, by.x="label", by.y="from", all=TRUE)
@
<<yeast_ex, echo=TRUE, fig.cap="Protein in protein interation network in yeast.", cache=FALSE>>=
ggplot(data = proteinnet, aes(from_id = label, to_id = to)) +
  geom_net(alpha=0.25, ealpha = .1, colour = 'magenta', layout = 'random',
           layout.par = list(dist = 'uniang')) +
  theme_net()
@
